Validation of Visual Statistical Inference, with Application to Linear Models

### 2012-04-19 paper_jasa.tex
some small questions - Mahbub, could you try to address those? thanks!

\begin{dfn} \label{dfn:power}
For a lineup of $m$ plots the power of \blue{a visual test} $T$
%$\theta$
 is defined as 
    \begin{equation*}
      \text{Power}_T(\theta)= 
        \begin{cases} 
              \text{Type-I error}=\frac1m & \text{if $\theta \in \Theta_0$,} \\
              Pr(\text{Reject } H_0) &\text{if $\theta \in \Theta^c_0$.}
        \end{cases}
    \end{equation*}
\end{dfn}

\red{HH: let's try to keep the power discussion as general as possible, and only use regression as an example.}

@@

When $K$ individuals evaluate a lineup plot independently, the number of successful evaluations, $U \sim \text{Binom} (K,1/m)$  under $H_0$. This leads us to obtain the probability $$Pr(U \ge u)= \sum_{k \ge u}^K {{K \choose k} (\frac{1}{m})^k(1-\frac 1m)^{(K-k)}}$$ where $u$ is the observed number of successful evaluations. We use this probability to  define $p$-value for visual test $T_{\theta}$ as in definition \ref{dfn:pval}.
\begin{dfn} \label{dfn:pval}
The $p$-value associated with the decision of a visual test $T_{\theta}$ is given by 
    \begin{equation*}
        \begin{cases} 
              p-value \le Pr(U \ge u)    & \text{when reject $H_0$,} \\
              p-value > 1-Pr(U \ge u)  & \text{when fail to reject $H_0$}
        \end{cases}
    \end{equation*}
\end{dfn}
% HH: I think this is covered by making power a property of the test
% In general,  $Pr(\text{Reject } H_0)$ is determined by the type of test being conducted.

\red{HH: We need to define p values corresponding to the data shown in plots.  MM: $p_D$ is what we use for this, right?}

%\red{HH: the following paragraph needs some adjustment in terms of t and $\theta$ - could you try to take of that, Mahbub?}\\

>>>>

\begin{dfn} \label{dfn:power}
For a lineup of $m$ plots the power of \blue{a visual test} $T$ is defined as the probability to reject the null hypothesis for a given parameter value $\theta$:
    \begin{equation*}
      \text{Power}_T(\theta)= 
        \begin{cases} 
              \text{Type-I error}=\frac1m & \text{if $\theta \in \Theta_0$,} \\
              Pr(\text{Reject } H_0) &\text{if $\theta \in \Theta^c_0$.}
        \end{cases}
    \end{equation*}
\end{dfn}

@@

When $K$ individuals evaluate a lineup plot independently, the number of successful evaluations, $U \sim \text{Binom} (K,1/m)$  under $H_0$. This leads us to obtain the probability $$Pr(U \ge u)= \sum_{k \ge u}^K {{K \choose k} \left(\frac{1}{m}\right)^k\left(1-\frac 1m\right)^{(K-k)}}$$ where $u$ is the observed number of successful evaluations. We use this probability to  define the $p$-value for visual test $T_{\theta}$ as follows:
\begin{dfn} \label{dfn:pval}
The $p$-value associated with the decision of a visual test $T_{\theta}$ is given by 
\red{HH: Why is the $p$ value not just $Pr(U \ge u)$ ? (We need to modify this a bit with respect to the rejection region $R$, but there should not be a difference in terms of whether we reject or accept. }

    \begin{equation*}
        \begin{cases} 
              p\text{-value} \le Pr(U \ge u)    & \text{when reject $H_0$,} \\
              p\text{-value} > 1-Pr(U \ge u)  & \text{when fail to reject $H_0$}
        \end{cases}
    \end{equation*}
\end{dfn}

%\red{HH: the following paragraph needs some adjustment in terms of t and $\theta$ - could you try to take of that, Mahbub?}\\
\red{For the following paragraph, we wanted to get rid of the absolute value of $t$ and instead look at $t \in R$ and $t \in R^c$.}
